\centering{Follow up on the incoherent t, t'}

### 2017-04-28 eg6-letters/NIM/EG6_RTPC_NIM.tex

We detail here the different regions shown in figure~\ref{fig:RTPC_1_4} starting 
from the beam line and towards larger radius:\\
\begin{itemize}
   \item First, the 6 atm helium-4 target extends along the beam line axis, it 
      is 284~mm long with a 3~mm radius wall made of a 27-$\mu$m-thick Kapton.
   \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o ller electrons scattered by the beam. This 
      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
      and electronically grounded.
   \item The second gap region extends between 20~mm and 30~mm and is filled with a 
      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
      serves as the cathode. {\bf \color{red} What Voltage ?}
   \item The drift region is filled with the same Ne-DME gas mixture and extends 
      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
      from the beam axis. The electric field in this region is around 500~V/cm 
      {\bf \color{red} Give exact value.} and perpendicular to the beam.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
      represents the anode. {\bf \color{red} What bias voltage ?}
   \item The readout board has an internal radius of 69~mm and collects charge
     from the GEMs. Preamplifiers are plugged directly on its outer side and
     transmit the signal to the data acquisition electronics.
\end{itemize}

>>>>

We detail here the different regions shown in figure~\ref{fig:RTPC_1_4} starting 
from the beam line and towards larger radius:\\
\begin{itemize}
   \item First, the 6 atm helium-4 target extends along the beam line axis, it 
      is 284~mm long with a 3~mm radius wall made of a 27-$\mu$m-thick Kapton.
   \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o ller electrons scattered by the beam. This 
      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
      and electronically grounded.
   \item The second gap region extends between 20~mm and 30~mm and is filled with a 
      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
      serves as the cathode and is set at 4260~V.
   \item The drift region is filled with the same Ne-DME gas mixture and extends 
      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
      from the beam axis. The electric field in this region is about 550~V/cm 
      and perpendicular to the beam.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600 V/cm) electric field between the GEM foils. A 
      275~V bias is applied to each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charge
     from the GEMs. Preamplifiers are plugged directly on its outer side and
     transmit the signal to the data acquisition electronics.
\end{itemize}

### 2017-04-28 for_eg6_group/t_tprime_April_2017/Incoh.tex

\section{$t'$ correction}
One can see from the free proton DVCS sample, figure \ref{fig:tprime_e1dvcs2}, 
that $t'$ is slightly shifted compared to $t$, which is considered as the true 
value in the free proton case. This shift in $t'$ is mainly induced by the 
radiative effects on the leptons. Before considering $t'$ in the incoherent EG6 
analysis, $t'$ has to be corrected and the reconstructed free proton 
asymmetries have to be verified in order to estimate the associated systematic 
uncertainties. Figure \ref{fig:corrections_tprime_e1dvcs2} presents the 
distributions of $t-t'$ as a function of $t'$ for the free proton DVCS sample 
from E1-DVCS2 data before and after correcting $t'$. In figure 
\ref{fig:after_tprime_e1dvcs2}, the distributions of figure 
\ref{fig:tprime_e1dvcs2} are shown after the $t'$ corrections.

\begin{figure}[h!]
\centering
\includegraphics[height=10.0cm]{fig/before_corrections_tprimet_t_InCoh.pdf}
\includegraphics[height=10.0cm]{fig/after_corrections_tprimet_t_InCoh.pdf}
\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
sample BEFORE correcting $t'$. The red line is the extracted correction for 
$t'$. On bottom: $t-t'$ as a function of $t'$ after correcting $t'$.}
\label{fig:corrections_tprime_e1dvcs2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
caption of figure \ref{fig:tprime_eg6} for plots description.}
\label{fig:after_tprime_e1dvcs2}
\end{figure}

@@

\section{EG6 Incoherent DVCS channel}
Here we apply the $t'$ corrections that were extracted from the free proton 
asymmetries  to the EG6 incoherent DVCS channel. Then, the asymmetries using 
$t$ are compared to the ones reconstructed using the corrected $t'$. The 
results are presented in figures \ref{fig:alu} and \ref{fig:alu90}.

\begin{figure}[tb]
   \centering
\includegraphics[width=15cm]{fig/ALU_phi_p_Q2.pdf}
\includegraphics[width=15cm]{fig/ALU_phi_p_x.pdf}
\includegraphics[width=15cm]{fig/ALU_phi_p_t.pdf}
\caption{The EG6 incoherent $A_{LU}$ as a function of $\phi$. Results are 
   presented for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle 
panel), and $t$ bins (bottom panel) using $t$ in black points and using the 
corrected $t'$ in red points.  The red curves are the results of our fits with 
the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
   \centering
\includegraphics[width=12cm]{fig/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=12cm]{fig/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=12cm]{fig/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The EG6 incoherent $Q^{2}$ (left), $x_{B}$ (middle), and 
$t$-dependencies (right) of the $A_{LU}$ at $\phi$~=~90$^{\circ}$ using $t$ in 
black points and using the corrected $t'$ in red points. }
\label{fig:alu90}
\end{figure}

\section{Conclusions}
We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
using the virtual and the final state real photons with corrections based on 
similar analysis on the free proton DVCS sample using the same setup of CLAS 
detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
slight changes using $t'$ rather than $t$, while the effect is bigger on the 
t-dependence, with overall changes are compatible with the statistical error 
bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
added to the EG6 incoherent asymmetries.

>>>>

\section{$t'$ corrections}
One can see from the free proton DVCS sample, figure \ref{fig:tprime_e1dvcs2}, 
that $t'$ is slightly shifted compared to $t$, which is considered as the true 
value in the free proton case. This shift in $t'$ is mainly induced by the 
radiative effects on the leptons. Before considering $t'$ in the incoherent EG6 
analysis, $t'$ has to be corrected and the reconstructed free proton 
asymmetries have to be verified in order to estimate the associated systematic 
uncertainties. Figure \ref{fig:corrections_tprime_e1dvcs2} presents the 
correlation between $t$ and $t'$ with proposed correcting functions.

\begin{figure}[h!]
\centering
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_2.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_3.pdf}
\caption{On top and middle: $t-t'$ as a function of $t'$ for the E1-DVCS2 free 
proton DVCS sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$.  The red 
lines are proposed correction functions for $t'$.}
\label{fig:corrections_tprime_e1dvcs2}
\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
%\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
%caption of figure \ref{fig:tprime_eg6} for plots description.}
%\label{fig:after_tprime_e1dvcs2}
%\end{figure}

@@

\section{EG6 Incoherent DVCS channel}
Here we apply the $t'$ corrections that were extracted from the free proton 
asymmetries to EG6 incoherent DVCS channel. Then, the asymmetries using $t$ are 
compared to the ones reconstructed using the corrected $t'$. The results are 
presented in figures \ref{fig:alu} and \ref{fig:alu90}.

Note: In black are the bins in $t$, in Red, blue and brown are the bins in $t'$ 
using the corrections presented in figure \ref{fig:corrections_tprime_e1dvcs2}, 
respectively.

\begin{figure}[tb]
   \centering
\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_Q2.pdf}
\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_x.pdf}
\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_t.pdf}
\caption{The EG6 incoherent $A_{LU}$ as a function of $\phi$. Results are 
   presented for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle 
   panel), and $t$ bins (bottom panel) using $t$ in black points and using the 
   corrected $t'$ in red points.  The red curves are the results of our fits 
   with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
   \centering
\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The EG6 incoherent $Q^{2}$ (left), $x_{B}$ (middle), and 
$t$-dependencies (right) of the $A_{LU}$ at $\phi$~=~90$^{\circ}$ using $t$ in 
black points and using the corrected $t'$ in red points. }
\label{fig:alu90}
\end{figure}

%\section{Conclusions}
%We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
%using the virtual and the final state real photons with corrections based on 
%similar analysis on the free proton DVCS sample using the same setup of CLAS 
%detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
%slight changes using $t'$ rather than $t$, while the effect is bigger on the 
%t-dependence, with overall changes are compatible with the statistical error 
%bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
%are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
%added to the EG6 incoherent asymmetries.
